\documentclass[a4paper,12pt]{amsart}

\input{preambles.tex}

\begin{document}

% Top matter
\title[Project Plan]{Project Plan for the Course COMP1110 -- Group D08}
% Authors, in alphabetical order by surname
%%
\newcommand{\cBanh}{C. Banh}
\author[\cBanh]{Chun Hei Banh}
\address{\cBanh, [Programme], [UID], \href{mailto:??@connect.hku.hk}{\texttt{??@connect.hku.hk}}}
%
\newcommand{\sLiu}{S. Liu}
\author[\sLiu]{Sze Pok Liu}
\address{\sLiu, [Programme], [UID], \href{mailto:u3658945@connect.hku.hk}{\texttt{u3658945@connect.hku.hk}}}
%
\newcommand{\jShing}{J. Shing}
\author[\jShing]{Zhan Ho Jacob Shing}
\address{\jShing, BEng(CompSc), 3036228892, \href{mailto:jacobszh@connect.hku.hk}{\texttt{jacobszh@connect.hku.hk}}}
%
\newcommand{\yYe}{Y. Ye}
\author[\yYe]{Yubing Ye}
\address{\yYe, [Programme], [UID], \href{mailto:u3629150@connect.hku.hk}{\texttt{u3629150@connect.hku.hk}}}
%
\newcommand{\yZhang}{Y. Zhang}
\author[\yZhang]{Yikun Zhang}
\address{\yZhang, BEng(CompSc), 3036482333, \href{mailto:pzdmmsd@connect.hku.hk}{\texttt{pzdmmsd@connect.hku.hk}}}
%%
\date{21 March 2026}
\maketitle

% BODY

\section{Topic Selection \& Introduction}

The group has selected the topic \textbf{B. Smart Public Transport Advisor} for the project.
For the project, the group will implement a route planner with the focus for pedestrian navigation within the campus of The University of Hong Kong (HKU).
To achieve that, the group will model the campus as an undirected multigraph as defined mathematically by:
\begin{equation} \label{eq:graph}
    G=(V,E),
\end{equation}
where for each vertex $v \in V$, $v$ represents a key location on the campus, such as a building entrance, a canteen, etc.;
and for each edge $e \in E$ represents an undirected path between two distinct vertices.
In addition to the graph structure, each edge will have a set of attributes, such as the average walking time, type of path (e.g., slope, stairs, etc.), etc.
The details of what attributes to include will be determined during the design phase of the project.

\section{Review of Existing Solutions}

For researching purposes, the group will review three types of existing solutions, each with two examples:
\begin{enumerate}
    \item \textbf{General purpose route planners}: Google Maps, Citymapper;
    \item \textbf{Transportation-specific route planners}: MTR Mobile App, HKBUS.app; and
    \item \textbf{Static navigation systems}: HKU campus map, On-campus navigation signages.
\end{enumerate}
The examples will be evaluated across several dimensions, such as easiness of use, specificity for pedestrian navigation, etc.
The conclusions drawn from the comparison shall be used to fine-tune the design of our own route planning implementation.

\section{Task Decomposition, Assignments \& Timeline}

The project will be decomposed into three phases: \textbf{Research \& Design}, \textbf{Implementation}, and \textbf{Test \& Evaluation}, each with its dedicated tasks.
Each task has a defined timeline and expected deliverables, which will be detailed in the following subsections.

\subsection{Task Decomposition}

\end{document}
